---
title: 'Developing Data Products: Course Project'
author: "Vicky C"
date: 'Aug 8, 2022'
output: ioslides_presentation
---

## Overview

In this project, we will do two things:

1. Create a Shiny application and deploy it on Rstudio's servers

2. Use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application

This application creates a histogram that displays the number of times an iris flower falls within a certain petal size. The user can choose the dimension, either petal length or width.

The link for the shiny app can be found [here](http://127.0.0.1:7192/) and the code can be found [here](https://github.com/practicingR/Course-9-Project).

## Dataset

This shiny app focuses on the petal.length and petal.width columns to plot in the histogram.
```{r}
head(iris)
```

## UI Code

```{r, echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}

# Data Processing for Iris dataset

library(shiny)
library(ggplot2)
library(dplyr)
irisData <- iris

# Define UI for application that creates a histogram

shinyUI(fluidPage(
  selectInput(inputId = "dimToPlot", label="Plot Dimension:",
              choices = c("Length","Width")),
  plotOutput(outputId = "distPlot")
))
```

## Server Code

```{r, echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
# Define server logic required to draw a histogram
shinyServer(function(input, output) {
  
  column <- reactive({paste0("Petal.",input$dimToPlot)})
  data <- eventReactive(input$dimToPlot, {
    irisData %>% 
      select(column()) %>%
      filter(get(column()) < 2)
  })
  
  # Histogram output
  output$distPlot <- renderPlot({
    ggplot(environment = environment(),
           data = data(), 
           aes_string(x = column())) +
      geom_histogram(color="white", fill="purple",bins = 10,boundary=0) 
  })
  
})

```
